Statistical quantification of confounding bias in predictive modelling

### 2022-04-22 fig/raw/emp_abide_motion_reg_full.tex
manuscript revised

\enlargethispage{100cm}
% Start of code
\begin{tikzpicture}[>=latex',line join=bevel,]
%%
\node (c) at (27.0bp,18.0bp) [draw,ellipse] {c};
  \node (y) at (158.0bp,53.0bp) [draw,ellipse] {y};
  \node (yhat) at (339.0bp,18.0bp) [draw,ellipse] {<<y\&\#770;>>};
  \draw [] (c) ..controls (75.327bp,30.841bp) and (109.82bp,40.199bp)  .. (y);
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (92.5bp,47.5bp) node {0.028};
  \draw [] (c) ..controls (74.615bp,14.069bp) and (104.67bp,11.894bp)  .. (131.0bp,11.0bp) .. controls (196.05bp,8.7922bp) and (272.59bp,13.206bp)  .. (yhat);
  \draw (158.0bp,18.5bp) node {0.359};
  \draw [dashed] (y) ..controls (218.38bp,41.389bp) and (278.81bp,29.573bp)  .. (yhat);
  \draw (248.5bp,50.5bp) node {0.02 (p=0.1)};
%
\end{tikzpicture}
% End of code

>>>>

\enlargethispage{100cm}
% Start of code
\begin{tikzpicture}[>=latex',line join=bevel,]
%%
\node (c) at (27.0bp,18.0bp) [draw,ellipse] {c};
  \node (y) at (158.0bp,53.0bp) [draw,ellipse] {y};
  \node (yhat) at (372.0bp,18.0bp) [draw,ellipse] {<<y\&\#770;>>};
  \draw [] (c) ..controls (75.327bp,30.841bp) and (109.82bp,40.199bp)  .. (y);
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (92.5bp,47.5bp) node {0.028};
  \draw [] (c) ..controls (74.615bp,14.069bp) and (104.67bp,11.894bp)  .. (131.0bp,11.0bp) .. controls (208.9bp,8.3558bp) and (301.06bp,13.31bp)  .. (yhat);
  \draw (158.0bp,18.5bp) node {0.062};
  \draw [dashed] (y) ..controls (225.43bp,42.033bp) and (304.96bp,28.903bp)  .. (yhat);
  \draw (265.0bp,52.5bp) node {0.031 (p=0.001*)};
%
\end{tikzpicture}
% End of code

### 2022-04-22 fig/raw/emp_abide_site_reg_partial.tex
manuscript revised

\enlargethispage{100cm}
% Start of code
\begin{tikzpicture}[>=latex',line join=bevel,]
%%
\node (c) at (27.0bp,18.0bp) [draw,ellipse] {c};
  \node (y) at (188.5bp,53.0bp) [draw,ellipse] {y};
  \node (yhat) at (341.0bp,18.0bp) [draw,ellipse] {<<y\&\#770;>>};
  \draw [] (c) ..controls (82.887bp,30.044bp) and (132.87bp,41.011bp)  .. (y);
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (92.5bp,43.5bp) node {0.019};
  \draw [dashed] (c) ..controls (74.615bp,14.069bp) and (104.67bp,11.894bp)  .. (131.0bp,11.0bp) .. controls (182.08bp,9.2662bp) and (194.92bp,9.1009bp)  .. (246.0bp,11.0bp) .. controls (269.06bp,11.857bp) and (295.23bp,13.894bp)  .. (yhat);
  \draw (188.5bp,18.5bp) node {0.05 (p=0.009*)};
  \draw [] (y) ..controls (242.32bp,40.716bp) and (287.48bp,30.214bp)  .. (yhat);
  \draw (280.0bp,42.5bp) node {0.17};
%
\end{tikzpicture}
% End of code

>>>>

\enlargethispage{100cm}
% Start of code
\begin{tikzpicture}[>=latex',line join=bevel,]
%%
\node (c) at (27.0bp,18.0bp) [draw,ellipse] {c};
  \node (y) at (193.0bp,53.0bp) [draw,ellipse] {y};
  \node (yhat) at (359.0bp,18.0bp) [draw,ellipse] {<<y\&\#770;>>};
  \draw [] (c) ..controls (83.822bp,29.913bp) and (136.23bp,41.098bp)  .. (y);
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (92.5bp,42.5bp) node {0.019};
  \draw [dashed] (c) ..controls (74.615bp,14.069bp) and (104.67bp,11.894bp)  .. (131.0bp,11.0bp) .. controls (186.08bp,9.1305bp) and (199.92bp,9.1305bp)  .. (255.0bp,11.0bp) .. controls (281.33bp,11.894bp) and (311.39bp,14.069bp)  .. (yhat);
  \draw (193.0bp,18.5bp) node {0.052 (p=0.003*)};
  \draw [] (y) ..controls (249.82bp,41.087bp) and (302.23bp,29.902bp)  .. (yhat);
  \draw (293.5bp,42.5bp) node {0.161};
%
\end{tikzpicture}
% End of code
